---
title: "Mini Project 4"
author: "Kerry LeCure, Libby Leung, Madeleine Hickman"
date: "11/27/2017"
output: html_document
---
```{r, message=FALSE}
library(mdsr) 
library(RMySQL) 
library(tidyverse)
library(ggthemes) 
db <- dbConnect_scidb(dbname = "imdb") 
```
```{r}
adventure <- db %>% 
  dbGetQuery("SELECT DISTINCT mi.movie_id, t.title, t.production_year, mi.info
             FROM aka_title t
             JOIN movie_info mi ON mi.movie_id = t.movie_id
             JOIN movie_companies mc ON mc.movie_id = mi.movie_id
             JOIN company_name cn ON cn.id = mc.company_id
             WHERE mi.info_type_id = 3
             AND mi.info = 'Adventure'
             AND t.kind_id = 1
             AND cn.country_code = '[us]'
             AND NOT (t.id IS NULL OR
             t.title IS NULL OR
             t.kind_id IS NULL OR
             t.production_year IS NULL OR
             mi.movie_id IS NULL OR
             mi.info IS NULL OR
             cn.country_code IS NULL)
             AND t.production_year BETWEEN 1900 AND 2017
             ORDER BY t.production_year;")
```
```{r}
adventuremovies <- adventure %>%
  group_by(production_year) %>%
  summarize(count = n())
```
```{r}
ggplot(adventuremovies, aes(x = production_year, y = count)) +
  geom_bar(stat = "identity") +
  labs(x = "Year", y = "Number of Adventure Movies Produced") +
  geom_vline(xintercept = 1981) +
  annotate("text", x = 1960, y = 400, label = "first Indiana Jones\nmovie released")
```

Lede.

Adventure movies are among the most popular movies, especially in the box office in terms of revenue, alongside comedy movies and action movies.<sup>1</sup> The ticket shares reflect this, and in a period from 1995 to 2017, they have had a share of 27.7% of all ticket sales.<sup>2</sup> In an interactive graph provided by www.the-numbers.com (http://www.the-numbers.com/live/cont/market/items_all_market_share_graph_iframe.php?movie_od_name_term=genre&cache_annual_postfix=genres&max_items=7&graph_category_text_plural=Genres), a pattern of ticket sales is similar to the number of adventure movies produced per year.

<sup>1</sup>https://www.statista.com/statistics/188658/movie-genres-in-north-america-by-box-office-revenue-since-1995/</br>
<sup>2</sup> http://www.the-numbers.com/market/genres